Appendix S1

### 2023-10-31 manuscript/supplementaryRW.Rmd
changing appendix name

---
title: "Appendix"
subtitle: "Tree regeneration in models of forest dynamics: a key priority for further research  ECOSPHERE"
author: 
- Olalla Díaz-Yáñez,
- Yannek Käber,
- Tim Anders,
- Friedrich Bohn,
- Kristin H. Braziunas,
- Josef	Brůna,
- Rico Fischer,
- Samuel M. Fischer,
- Jessica Hetzer,
- Thomas Hickler,
- Christian	Hochauer,
- Manfred J. Lexer,
- Heike	Lischke,
- Paola	Mairota,
- Ján Merganič,
- Katarina Merganičová,
- Tobias Mette,
- Marco Mina,
- Xavier Morin,
- Mats Nieberg,
- Werner Rammer,
- Christopher P.O. Reyer,
- Simon	Scheiter,
- Daniel Scherrer,
- Harald Bugmann
date: ""
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    latex_engine: xelatex
    extra_dependencies: ["flafter", "float", "subfig"]
    toc: yes
bibliography: Regeneration.bib
link-citations: yes
linkcolor: blue
csl: chicago-author-date.csl
editor_options: 
  markdown: 
    wrap: 72
fontsize: 12pt
linestretch: 2
header-includes:
- \usepackage[left]{lineno}
- \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
- \usepackage{fontspec}
- \setmainfont{Times New Roman}
---

@@

sigDiff <- readr::read_csv(here::here("figures", "sigH7_10.csv"))
sigDiff$p.adj <- NULL
colnames(sigDiff) <- c("model", "y", "Group 1", "Group 2", "p", "p.signif")

>>>>

---
title: "Appendix S1"
subtitle: "Tree regeneration in models of forest dynamics: a key priority for further research  ECOSPHERE"
author: 
- Olalla Díaz-Yáñez,
- Yannek Käber,
- Tim Anders,
- Friedrich Bohn,
- Kristin H. Braziunas,
- Josef	Brůna,
- Rico Fischer,
- Samuel M. Fischer,
- Jessica Hetzer,
- Thomas Hickler,
- Christian	Hochauer,
- Manfred J. Lexer,
- Heike	Lischke,
- Paola	Mairota,
- Ján Merganič,
- Katarina Merganičová,
- Tobias Mette,
- Marco Mina,
- Xavier Morin,
- Mats Nieberg,
- Werner Rammer,
- Christopher P.O. Reyer,
- Simon	Scheiter,
- Daniel Scherrer,
- Harald Bugmann
date: ""
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    latex_engine: xelatex
    extra_dependencies: ["flafter", "float", "subfig"]
    toc: yes
bibliography: Regeneration.bib
link-citations: yes
linkcolor: blue
csl: chicago-author-date.csl
editor_options: 
  markdown: 
    wrap: 72
fontsize: 12pt
linestretch: 2
header-includes:
- \usepackage[left]{lineno}
- \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
- \usepackage{fontspec}
- \setmainfont{Times New Roman}
---

@@

sigDiff <- readr::read_csv(here::here("figures", "sigH7_10.csv"))
sigDiff$p.adj <- NULL
sigDiff$p <- NULL
sigDiff$method <- NULL
colnames(sigDiff) <- c("model", "y", "Group 1", "Group 2", "p", "p.signif")
